### 2015-03-23 doc/thesis/typedlua.tex
Final touches before sending to juries

We use a double arrow instead of a single arrow because it is
syntactic sugar for defining the type of methods,
as it includes an implicit first type \texttt{self}.
The double arrow can appear only inside the declaration of
interfaces and userdata, which we will introduce in the next section.

@@

In a \texttt{setmetatable} expression
\texttt{setmetatable(e:(el),\{\string_\string_index = id\})},
if the expression \texttt{e:(el)} has a \emph{closed} table type \texttt{t},
\texttt{id} has type \texttt{self}, and the type bound to \texttt{self}
is a subtype of \texttt{t}, then the expression has type \texttt{self}.
Note how we can use this rule to call the constructor of \texttt{Shape}
inside the overridden constructor.
A limitation of this class system is that the overridden constructor
must be a subtype of the original constructor,
so the type of \texttt{radius} has to be quite permissive.
Also note that this is the only form of refinement that allows
changing the type of a table field, if the new type is a subtype
of the previous type.

>>>>

We use a double arrow instead of a single arrow because it is
syntactic sugar for defining the type of methods,
as it includes an implicit first input type \texttt{self}.
The double arrow can appear only inside the declaration of
interfaces and userdata, which we will introduce in the next section.

@@

In a \texttt{setmetatable} expression
\texttt{setmetatable(e,\{\string_\string_index = id\})},
if the expression \texttt{e} has a \emph{closed} table type \texttt{t},
\texttt{id} has type \texttt{self}, and the type bound to \texttt{self}
is a subtype of \texttt{t}, then the expression has type \texttt{self}.
Note how we can use this rule to call the constructor of \texttt{Shape}
inside the overridden constructor.
A limitation of this class system is that the overridden constructor
must be a subtype of the original constructor,
so the type of the input parameter \texttt{radius} has to be quite permissive.
Also note that this is the only form of refinement that allows
changing the type of a table field, if the new type is a subtype
of the previous type.
